### 2023-06-20 python_excel_ite.tex
working on intro section

\usepackage[most]{tcolorbox}
\usepackage{minted}
\tcbuselibrary{minted} % tcolorbox minted library, required to use the "minted" tcb listing engine (this library is not loaded by the option [most])
%\usepackage{minted} % Allows input of raw code, such as Python code
\usepackage[colorlinks]{hyperref} % ALWAYS load this package LAST

@@

% The opening part of the what-if notebook has some language for the motivation behind this module.
% TODO - opening should really grab reader
Spreadsheet based modeling has transformed the teaching of management science in business schools. The late 1990's saw the first editions of game changing textbooks \cite{ } focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science (TMS) with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education journal \cite{bibid}. I attended TMS III at Indiana University and left with numerous ideas that influenced my own spreadsheet based modeling course. The next few decades saw numerous textbooks and teaching papers that prominently featured spreadsheet based modeling.

Despite numerous calls for and predictions of the eradication of spreadsheets from the business world,

Spreadsheet based modeling wave of the early 2000s. TMS conferences. Ground breaking textbooks such as Ragsdale and W\&A.
The first two issues of ITE are paper based on TMS 1 at Dartmouth in 1998. I attended TMS 3 in Bloomington in 2000.

First edition of Ragsdale was 1995 PMS was 1997.

@@

Python has continued to make inroads to analytical territory that was formerly dominated by Excel. The widely used Python data analysis library, Pandas, was created by Wes McKinney while working as a quantitative financial analyst. However, Python was mainly used for data wrangling, visualization and predictive modeling using various flavors of regression and tree based models. The blog \href{https://pbpython.com/}{Practical Business Python} written primarily by Chris Moffitt contributed greatly to making Python more accessible to business analytics practitioners through high quality posts that were extremely practical and useful. But, it got me to thinking. What about those things for which Excel is well suited such as building formula based models and doing sensitivity analysis on these models? What would those look like in Python?

@@

PBB blog

@@

Integrated or separate lit review section?

@@

% CASE 1: BiBTeX used to constantly update the references 
%   (while the paper is being written).
%\bibliographystyle{informs2014} % outcomment this and next line in Case 1
%\bibliography{<your bib file(s)>} % if more than one, comma separated

>>>>

\usepackage[most]{tcolorbox}
\usepackage{minted}
\tcbuselibrary{minted} % tcolorbox minted library, required to use the "minted" tcb listing engine (this library is not loaded by the option [most])
\usepackage[colorlinks]{hyperref} % ALWAYS load this package LAST

@@

Spreadsheet based modeling has transformed the teaching of management science in business schools over the past three decades. The late 1990's saw first editions of game changing textbooks \cite{winstonPracticalManagementScience2018,ragsdaleSpreadsheetModelingDecision2017} focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science (TMS) with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education journal \cite{bibid}. The next few decades saw numerous textbooks \cite{BusinessAnalyticsArt, BusinessAnalytics4th} and teaching papers \cite{INFORMSTransactionsEducation2014} that prominently featured spreadsheet based modeling.

Despite numerous calls for and predictions of the eradication of spreadsheets from the business world, Google "spreadsheets are evil"

Excel not a database and shouldn't be used as one. There are better data visualizaiton and exploration tools. There are better dashboarding tools. Spreadsheet errors are a huge problem. Version control and documentation issues. Data size limitations. External link problems. But, spreadsheets are still very well suited to what if type modeling due to their flexibility, numerous built in functions, integrated visualization capabilities and ubiquity

@@

Python has continued to make inroads to analytical territory that was formerly dominated by Excel. The widely used Python data analysis library, Pandas, was created by Wes McKinney while working as a quantitative financial analyst \cite{bibid}. However, Python was mainly used for data wrangling, visualization and predictive modeling using various flavors of regression and tree based models. The blog \href{https://pbpython.com/}{Practical Business Python} written primarily by Chris Moffitt contributed greatly to making Python more accessible to business analytics practitioners through high quality posts that were extremely practical and useful. But, it got me to thinking. What about those things for which Excel is well suited such as building formula based models and doing sensitivity analysis on these models? What would those look like in Python?

@@

@@

%TODO: Integrated or separate lit review section?

@@

% CASE 1: BiBTeX used to constantly update the references 
%   (while the paper is being written).
\bibliographystyle{informs2014} % outcomment this and next line in Case 1
\bibliography{python_excel.bib} % if more than one, comma separated
